### 2022-07-26 src/text/2-package-subsections/analysis.tex
Update analysis sub-package description
Use shortcuts more consistently
Add instruments IRF plot

\subsection{gammapy.analysis}
\label{ssec:gammapy-analysis}
\todo{Quentin, Axel...}

The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
common use cases identified in gamma-ray analyses. The classes and methods
included can be used in Python scripts, notebooks or as commands within IPython
sessions. The high-level user interface can also be used to automatise
workflows driven by parameters declared in a configuration file in YAML format.
This way a full analysis can be executed via a single command line taking the
configuration file as input.

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0...}

>>>>

\subsection{gammapy.analysis}
\label{ssec:gammapy-analysis}
The \code{gammapy.analysis} sub-module provides a  high-level interface for the most
common use cases identified in \gammaray analyses. The classes and methods
included can be used in Python scripts, notebooks or as commands within IPython
sessions. The high-level user interface can also be used to automatise
workflows driven by parameters declared in a configuration file in YAML format.
This way a full analysis can be executed via a single command line taking the
configuration file as input.

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that defines the common use cases identified. These
steps include the following: observations selection from the DataStore,  data
reduction, excess map computation, model fitting, flux-points estimation, and
light-curves production. The structure of the \code{Analysis} class allows to define
custom AnalysisStep, so ones could design and configure arbitrarily complex
wokflows. \todo{the latter is not true for v1.0..., include example YAML file?}

### 2022-07-26 src/text/2-package-subsections/catalog.tex
Use shortcuts more consistently
Add instruments IRF plot

\begin{table*}
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class Name & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
\end{table*}

\begin{figure}
	\import{code-examples/generated/}{gp_catalogs}
	\caption{Using gammapy.catalogs: Accessing underlying model, flux points and
		lightcurve from the Fermi-LAT 4FGL catalog for the blazar PKS 2155-304}
	\label{codeexample:data}
\end{figure}

>>>>

\begin{table*}[ht!]
    \begin{center}
        \begin{tabular}{llll}
         \hline
         Class Name & Shortcut & Description & Reference\\
         \hline
         \code{SourceCatalog3FGL} & \code{"3fgl"} & 3\textsuperscript{rd} catalog of \fermi sources & \cite{3FGL} \\
         \code{SourceCatalog4FGL} & \code{"4fgl"} & 4\textsuperscript{th} catalog of \fermi  sources & \cite{4FGL} \\
         \code{SourceCatalog2FHL} & \code{"2fhl"} & 2\textsuperscript{nd} catalog high energy \fermi  sources & \cite{2FHL} \\
         \code{SourceCatalog3FHL} & \code{"3fhl"} & 3\textsuperscript{rd} catalog high energy \fermi  sources & \cite{3FHL} \\
         \code{SourceCatalog2HWC} & \code{"2hwc"} & 2\textsuperscript{nd} catalog of \hawc sources & \cite{2HWC} \\
         \code{SourceCatalog3HWC} & \code{"3hwc"} & 3\textsuperscript{rd} catalog of \hawc sources & \cite{3HWC} \\
         \code{SourceCatalogHGPS} & \code{"hgps"} & \hess Galactic Plane Survey catalog & \cite{HGPS} \\
         \code{SourceCatalogGammaCat} & \code{"gammacat"} & Open source data collection & \citep{gamma-cat} \\
         \hline
         \end{tabular}
    \end{center}
    \label{tab:catalogs}
    \caption{Overview of supported catalogs in \code{gammapy.catalog}.}
\end{table*}

\begin{figure}
	\import{code-examples/generated/}{gp_catalogs}
	\caption{Using \code{gammapy.catalogs} to access the underlying model, flux points and
		light-curve from the \fermi 4FGL catalog for the blazar PKS 2155-304}
	\label{codeexample:data}
\end{figure}

### 2022-07-26 src/text/2-package.tex
Add instruments IRF plot

\section{Gamma-ray Data Analysis}
\label{sec:gammaray-data-analysis}

% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

>>>>

\section{Gamma-ray Data Analysis}
\label{sec:gammaray-data-analysis}
%
\begin{figure*}[ht!]
	\centering
	\includegraphics[width=1.\textwidth]{figures/irfs.pdf}
	\caption{
		Example instrument response functions of some experiments and
        observatories for which \gammapy can analyse data. The \cta IRFs
        are from the prod5 production. The \hess IRFs are from the DL3 DR1,
        using observation ID 033787. The point spread function shows the 65\&
        containment radius of the PSF. The \fermi IRFs are from \textit{pass8}.
        \todo{Add more instruments? HAWC? MAGIC?}
    }
	\label{fig:irfs}
\end{figure*}
%
% This might not be the bast place compared to introduction
The data reduction process in \gammaray astronomy is usually split into two parts.
The first one deals with the data processing from camera measurement, calibration, event
reconstruction and selection to yield a list of reconstructed \gammaray event candidates.
This sequence, sometimes referred to as low-level analysis, is usually very specific to
a given observation technique and even to a given instrument.

### 2022-07-26 src/text/3-applications-subsections/population-studies.tex
Use title case consistently
Add instruments IRF plot

\subsection{Surveys, catalogs, and population studies}
\label{ssec:surveys-catalogs-and-population-studies}

Sky surveys have a large potential for new source detections, and new phenomena
discovery. They also offer less selection bias to perform source population
studies over a large set of coherently detected and modelled objects. Early
versions of \textit{gammapy} were developed in parallel of the preparation of
the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
	2018A&A...612A...3H}.

@@

In short the production of catalogs from \gammaray surveys can be divided in
four main steps : data-reduction; object detection; model fitting and model
selection; associations and classification. The IACTs data-reduction step is
done in the same way than described in the previous sections but scale-up to
few thousand of observations. The object detection step consists a minima in
finding local maxima in the significance, or TS maps,  given by the
ExcessMapEstimator, or TSMapEstimator, respectively.  Further refinements can
include for example  filtering and detection on these maps with techniques from
scikit-image package~\citep{scikit-image}, and outlier detection from
scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it
reduces the spurious detections at this stage and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage gammapy.modeling.models offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
gaussian...), and spectral models (power-law, log-parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log-Likelihood between these two
hypotheses. For the association and classification step, that is tightly
connected to the population studies, we can a minima compare the fitted models
to the set of gammapy-ray catalogs available in gammapy.catalog. However
further multi-wavelength cross-matches are usually required to characterize the
sources.

>>>>

\subsection{Surveys, Catalogs, and Population Studies}
\label{ssec:surveys-catalogs-and-population-studies}

Sky surveys have a large potential for new source detections, and new phenomena
discovery. They also offer less selection bias to perform source population
studies over a large set of coherently detected and modelled objects. Early
versions of \gammapy were developed in parallel of the preparation of
the \hess Galactic plane survey catalog~\citep[HGPS][]{2018A&A...612A...1H} and
the associated PWN and SNR populations studies~\citep{2018A&A...612A...2H,
	2018A&A...612A...3H}.

@@

In short the production of catalogs from \gammaray surveys can be divided in
four main steps : data-reduction; object detection; model fitting and model
selection; associations and classification. The IACTs data-reduction step is
done in the same way than described in the previous sections but scale-up to
few thousand of observations. The object detection step consists a minima in
finding local maxima in the significance, or TS maps,  given by the
\code{ExcessMapEstimator}, or \code{TSMapEstimator}, respectively.  Further refinements can
include for example  filtering and detection on these maps with techniques from
scikit-image package~\citep{scikit-image}, and outlier detection from
scikit-learn package~\citep{scikit-learn}. Tests on simulations shown that it
reduces the spurious detections at this stage and then speed up the next step
as less objects will have to be fitted simultaneously. During the modelling
step each object is alternatively fitted with different models in order to
determine their optimal parameters, and the best-candidate model. The
subpackage gammapy.modeling.models offers a large variety of choice, and the
possibility to add custom models.  Several spatial models (point-source, disk,
gaussian...), and spectral models (power-law, log-parabola...) may be tested
for each object, so the complexity of the problem increases rapidly in regions
crowded with multiple extended sources. Finally an object is discarded if its
best-fit model is not significantly preferred over the null hypothesis (no
source) comparing the difference in log-Likelihood between these two
hypotheses. For the association and classification step, that is tightly
connected to the population studies, we can a minima compare the fitted models
to the set of gammapy-ray catalogs available in gammapy.catalog. However
further multi-wavelength cross-matches are usually required to characterize the
sources.
